%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Research Professional}
{ASSIST Research Lab, Florida Institute of Technology}
{Melbourne, FL}
{August 2021 - Present}
{
\begin{cvitems}
    \item Collaborated with Rockwell Collins on a NASA-funded project to formally verify the safety and logical correctness of a safety-critical autonomous agent system.
    \item Employed formal methods (e.g., theorem proving, model checking) to analyze agent behavior and guarantee desired properties.
    \item Contributed to ensuring the reliable and predictable operation of the autonomous system. (Development and deployment of a Soar-nuXmv translator)
    \item Developed a formal modeling approach for designing, maintaining, and supporting air and sea platform fiber optic communications technology as part of the "Critical Frequency Design" project funded by Naval Air Systems Command.
    \item Utilized formal methods (e.g., state-based models, temporal logics).
    \item Addressed the limitations of SysML for function-based modeling and reasoning by introducing an XML-based approach and developing the XMLSlim optimization algorithm.
    \item Developed and implemented formal verification methods (e.g., model checking, theorem proving) in projects like "Assuring Adaptive Learning-Enabled Increasingly Autonomous Systems" and "A BERT Approach on Transforming Engineering Requirements into SysML Diagrams using XML."
    \item Demonstrated ability to analyze system behavior and ensure safety properties through formal methods.
    \item Pursuing my thesis on formal generalization of common knowledge in transfer learning methods. 
\end{cvitems}
}
\cventry
{Graduate Research Assistant}
{IRI Research, Florida Institute of Technology}
{Melbourne, FL}
{May 2023 - August 2023}
{
\begin{cvitems}
% \item ASSIST Research Lab focuses on the design and development of assurance frameworks for mission-critical, safety-critical, and security-critical systems.
\item Proposed and implemented a framework using AI language models to automatically extract software requirements from source code ("Automated Framework to Extract Software Requirements from Source Code").
\item Proposed a novel automated framework that extracts software requirements directly from source code using LLMs APIs.
\item Supervised and coordinated with undergraduate students towards the development process.
\end{cvitems}
}

\end{cventries}